---
title: "Sensitivity Analysis on SSHISTX"
author: "Brendhan Givens"
date: "December 7, 2014"
output: html_document
---

**Use ggplot2.  It may reduce overlapping plots.**

```{r}
# Define parameters
set.seed(1111)
N = 1000
x <- rexp(N,5)
y <- runif(N,1.5,2.5)
z <- rnorm(N,1,0.1)
w <- c(x,y,z)
```

```{r,echo=FALSE}
source('histbreaks.R')
ph1 = "Using Sshistx"
ph2 = "Using Freedman-Diaconis's (FD)"
ph3 = "Using Sturges's"
ph4 = "Using Scott's"
```

# Inliers

```{r}
# Sensitivity to Inliers
n = c(10,30,50) # number of inliers
val = 1.4 # where inliers are placed
par(mfrow=c(2,2))
hist(w,breaks=sshistx(w),
     main=sprintf("%s, no inliers",ph1))
for (k in seq_along(n)) {
    w1 <- c(w,rep(val,n[k]))
    hist(w1,breaks=sshistx(w1),
         main=sprintf("%s, with %i inliers",ph1,n[k]))
}
```

Determination:  Needs regularization for a large number of inliers.

# Outliers

```{r}
# Sensitivity to Outliers
val = 4.0
par(mfrow=c(2,2))
hist(w,breaks=sshistx(w),
     main=sprintf("%s, no outliers",ph1),
     xlim=c(0,val))
for (k in seq_along(n)) {
    w1 <- c(w,rep(val,n[k]))
    hist(w1,breaks=sshistx(w1),
         main=sprintf("%s, with %i outliers",ph1,n[k]),
         xlim=c(0,val))
}

```

Determination:  Needs regularization for a large number of outliers.

## Population Size

```{r}
# Sensitivity to population size
p = c(1/10,1/4,1,3)*N
par(mfcol=c(2,length(p)))
for (k in seq_along(p)) {
    w1 = sample(w,p[k])
    hist(w1,breaks=sshistx(w1),
         main=sprintf("%s, Population = %i",ph1,p[k]))
    hist(w1,breaks="Scott",
         main=sprintf("%s, Population = %i",ph4,p[k]))
}
```

Need to fix titles.
Changes are not linear or smooth.

## Comparison of Normals for different populations

```{r}
v = rnorm(3*N)
par(mfcol=c(2,length(p)))
for (k in seq_along(p)) {
    v1 = sample(v,p[k])
    hist(v1,breaks=sshistx(v1),
         main=sprintf("%s, Normal, Population = %i",ph1,p[k]))
    hist(v1,breaks="Scott",
         main=sprintf("%s, Normal, Population = %i",ph4,p[k]))
}
```

Need to fix titles.
Smooth and good.

## Going towards asymptotic

```{r}
M = 1e5
par(mfrow=c(1,2))
r = rnorm(M)
hist(r,breaks=sshistx(r,N=200),
     main=sprintf("%s, Large Population",ph1)) # This takes a long time
hist(r,breaks="Scott",
     main=sprintf("%s, Large Population",ph4))
```

Slightly different than scott.  Looks good.
